---
title: "10-import"
output: html_notebook
---

## Load the libraries

Library list: 

```{r libraries_list}
library(readr)
library(rjson)
library(janitor)
library(assertr)
library(tidyverse)
library(lubridate)
library(glue)
library(scales)
```

## Load data

Now we can import the dataset and clean the names first.

```{r import data}
USvideos <- read_csv("data/USvideos.csv") %>%
  clean_names()
```

Now import the category name from JSON file.
```{r}
category_id = fromJSON(file = "data/US_category_id.json",  unexpected.escape = "error")
```

## Overview

For the operation in the future, having a overview can help us understand the dataset easily.

```{r overview}
dim(USvideos)
str(USvideos)
```

As we can see, there are 16 variables and 40949 observations in the original data. 

Variables | description
---|---
**video_id** | A unique string for each observation to identify the different videos.
**trending_date** | The date that each video be define as a trending video (appeared in  [top trending videos](https://www.youtube.com/feed/trending) page ).
**title** | The title of the video.
**channel_title** | The channel title that created by youtubers themselves.
**category_id** | The catebory number of each video where it was posted. If you need the name of each catebory, please check the JSON file.
**publish_time** | The excect time when youtuber posted the video.
**tags** | The tags youtuber defined for each video.
**views** | The number of views.
**likes** | The number of likes.
**dislikes** | The number of dislikes.
**comment_count** | The number of comments.
**thumbnail_link** | The thumbnail of each video cover.
**comments_disabled** | Viewers can comment or not.
**ratings_disabled** | viewers can rate the video or not.
**video_error_or_removed** | The video was removed or not.
**description** | The description of each video, created by youtubers.
